---
title: "Inference for Empirical Quantile-Based Estimators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inference for Empirical Quantile-Based Estimators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quantcdf.inference)
```

## Overview

The package implements estimation and inference for parameters of the form
$\theta_0 = E[F_Y^{-1}(F_Z(X))]$, as studied by Chhor, D'Haultfœuille,
L'Hour, and Mugnier (2026).

The estimator uses empirical distribution functions and the left-continuous
empirical quantile convention, including $F_Y^{-1}(0) = Y_{(1)}$.

## Simulate Data

```{r simulate-data}
set.seed(42)
d <- sim_dgp(500)

str(d)
head(d$Y)
head(d$X)
head(d$Z)
```

## Fit The Quantile-Based Estimator

The first three inputs are Sample 1, Sample 2, and Sample 3, corresponding to
$Y$, $X$, and $Z$ in the paper.

```{r estimation}
out <- fit(
  sample1 = d$Y,
  sample2 = d$X,
  sample3 = d$Z,
  method = c("no-split", "split", "ai", "bse", "bpc"),
  B = 1000,
  timings = TRUE
)
out$theta_hat
out$ci
```

The asymptotic methods are:

- `no-split`: full-sample plug-in variance estimator
- `split`: sample-splitting variance estimator
- `ai`: Athey-Imbens variance estimator

The split and no-split estimators use the varying bandwidth
$h_{n_2}(u) = \epsilon_{n_2}u(1-u)$, with default
$\epsilon_{n_2} = 1/\log(n_2)$. The Athey-Imbens method uses an Epanechnikov
density estimator for Sample 1 with $h_{AI} = 1.06 n_1^{-1/5}/\widehat{sd}(Y)$.

## Changes-in-Changes Contrast

`cic_fit()` estimates
`mean(Y11) - fit(sample1 = Y01, sample2 = Y10, sample3 = Y00)$theta_hat`.

```{r cic-fit}
Y11 <- d$Y + 0.5
cic <- cic_fit(
  Y11 = Y11,
  Y10 = d$X,
  Y01 = d$Y,
  Y00 = d$Z,
  method = c("no-split", "ai", "bse"),
  B = 1000
)
cic$theta_hat
cic$ci
```

For analytic methods, `cic_fit()` adds the independent repeated-cross-section
contribution of `Y11` on the same `sqrt(N)` asymptotic variance scale. For
bootstrap methods, each replication independently resamples all four samples
and recomputes the complete estimator.

## Panel Data Estimation

For paired samples, `panel_data = TRUE` remains available for `no-split` and
`split` in `fit()`.

```{r estimation-panel}
n_panel <- 400
sample1_panel <- rnorm(n_panel)
sample3_panel <- sample1_panel + rnorm(n_panel, sd = 0.5)
sample2_panel <- rnorm(300)

out_panel <- fit(
  sample1 = sample1_panel,
  sample2 = sample2_panel,
  sample3 = sample3_panel,
  method = c("no-split", "split"),
  panel_data = TRUE,
  timings = TRUE
)
out_panel$theta_hat
out_panel$ci
```

## S3 Helpers

```{r helpers}
coef(out)
confint(out)
summary(out)
summary(cic)
```
