---
title: "Inference for Empirical Quantile-Based Changes-in-Changes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inference for Empirical Quantile-Based Changes-in-Changes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cic.newassumptions.newvarianceestimator)
```

## Overview

`cic` estimates the Changes-in-Changes parameter and returns several types of confidence intervals.
The package performs basic input validation and emits clear warnings for common input issues.

In this vignette we use the built-in simulation helpers to show the full workflow:

1. generate data,
2. run the diagnostic check,
3. estimate the CiC parameter with several interval methods,
4. inspect the output,
5. visualize the confidence intervals.

## Simulate Data

```{r simulate-data}
set.seed(42)
d <- sim_dgp(500)

str(d)
head(d$Y)
head(d$X)
head(d$Z)
```

The simulation helpers are mainly intended for examples and Monte Carlo experiments.
They let you quickly reproduce the DGP used in the package documentation and tests.

## Input validation

The package will warn for non-vector inputs, many tied values, and invalid bandwidths.
Inspect warnings produced by `cic()` when running your data.

## Estimation

The `method` argument accepts one or several interval constructors.

```{r estimation}
fit <- cic(
  d$Y, d$X, d$Z,
  method = c("no-split", "split", "kde", "bse", "bpc"),
  B = 1000,
  timings = TRUE
)

fit
fit$theta_hat
fit$ci
```

If you only want to profile the runtime, set `timings = TRUE` and the function
will print elapsed time after each major computation block.

The first three methods are asymptotic constructions:

- `no-split`: full-sample plug-in variance estimator
- `split`: sample-splitting variance estimator
- `kde`: kernel-density-based variance estimator

The bootstrap methods are included for robustness checks and finite-sample comparisons:

- `bse`: bootstrap standard-error interval
- `bpc`: bootstrap percentile interval

## Compare Methods

When you request several methods at once, the results are returned in the order you asked for.

```{r compare-methods}
fit$ci[, c("method", "lower", "upper", "length")]
```

You can also compare the fitted object with its S3 helpers:

```{r helpers}
coef(fit)
confint(fit)
summary(fit)
```

## Visualization

The package provides a plot method to compare the confidence intervals visually.

```{r plot-fit, fig.width=7, fig.height=3.5}
## plotting has been removed from the package; print the CI table instead
print(fit$ci)
```

## Practical Notes

For empirical work, the main workflow is:

1. estimate with at least one asymptotic method,
2. compare with a bootstrap method if you want a robustness check,
3. report the chosen method and confidence level explicitly.

The vignette and README now follow the manuscript by Chhor, D'Haultfoeuille, L'Hour, and Mugnier rather than the older Athey-Imbens reference.
