---
title: "Inference for Empirical Quantile-Based Changes-in-Changes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inference for Empirical Quantile-Based Changes-in-Changes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cicinference)
```

## Overview

The `cicinference` package implements the estimation and inference framework developed by **Chhor, d'Haultfœuille, L'Hour, and Mugnier (2026)** in *"Asymptotic Properties of Empirical Quantile-Based Estimators"*. 

This framework generalizes the classic Changes-in-Changes (CiC) model to much weaker and more realistic conditions. Notably, it allows for unbounded outcome variables (e.g., wages, profits) and strictly weaker smoothness assumptions.

The package estimates the parameter $\theta_0 = E[F_Y^{-1}(F_Z(X))]$ and provides several types of robust asymptotic and bootstrap-based confidence intervals.

## Simulate Data

We can use the built-in simulation helper `sim_dgp` to generate cross-sectional data:

```{r simulate-data}
set.seed(42)
d <- sim_dgp(500)

str(d)
head(d$Y)
head(d$X)
head(d$Z)
```

## Input validation

The package will warn for non-vector inputs, many tied values, and invalid bandwidths.
Inspect warnings produced by `cic_inference()` when running your data.

## Estimation (Cross-Sectional Data)

The `method` argument accepts one or several interval constructors.

```{r estimation}
fit <- cic_inference(
  d$Y, d$X, d$Z,
  method = c("no-split", "split", "kde", "bse", "bpc"),
  B = 1000,
  timings = TRUE
)
fit$theta_hat
fit$ci
```

The first three methods are asymptotic constructions:

- `no-split`: full-sample plug-in variance estimator
- `split`: sample-splitting variance estimator
- `kde`: kernel-density-based variance estimator

The bootstrap methods (`bse` and `bpc`) are included for robustness checks.

## Panel Data Estimation

When working with panel data, the pre-treatment and post-treatment variables for the control group ($Z$ and $Y$) are paired (measured on the same individuals over two periods). Therefore, they must have the exact same length (`length(Y) == length(Z)`).

To trigger the panel-specific splitting and plug-in estimators derived by Chhor et al. (2026), set `panel_data = TRUE`:

```{r estimation-panel}
# Simulating a panel structure where Y and Z have matching lengths
n_panel <- 400
Y_panel <- rnorm(n_panel)
Z_panel <- Y_panel + rnorm(n_panel, sd = 0.5) # Paired baseline
X_panel <- rnorm(300)

fit_panel <- cic_inference(
  Y = Y_panel, 
  X = X_panel, 
  Z = Z_panel,
  method = c("no-split", "split"),
  panel_data = TRUE,
  timings = TRUE
)
fit_panel$theta_hat
fit_panel$ci
```

## Compare Methods

When you request several methods at once, the results are returned in a summary table.

```{r compare-methods}
fit$ci[, c("method", "lower", "upper", "length")]
```

You can also compare the fitted object with its S3 helpers:

```{r helpers}
coef(fit)
confint(fit)
summary(fit)
```

## Visualization

Print the CI table to compare the bounds across methods:

```{r plot-fit}
print(fit$ci)
```

## Practical Recommendations

Based on the theoretical results of Chhor et al. (2026):

1. **Use `split` (Sample-Splitting) for smaller samples**: It provides excellent coverage and avoids over-optimistic (too narrow) intervals when sample size is moderate.
2. **Compare with `bpc`**: Use the bootstrap percentile method as a finite-sample robustness check.
3. **Specify `panel_data = TRUE`** when your control group data is paired, to correctly account for the temporal correlation within subjects.
---